Fail Faster

### 2025-03-19 paper/paper.tex

All experiments were run on a 64-bit Linux machine with 264 GB RAM and an Intel Xeon Platinum 8375C CPU, running Ubuntu 24.04.1 LTS.
The \name library was implemented using the
4.14.1+BER MetaOCaml compiler variant.  All OCaml benchmarks
were compiled with \texttt{ocamlopt}, the native code compiler for OCaml, using compiler flag \texttt{-O3}.
The microbecnhmark

. \todo{Joe : Scala info ...}

>>>>

All experiments were run on a 64-bit Linux machine with 264 GB RAM and an Intel Xeon Platinum 8375C CPU, running Ubuntu 24.04.1 LTS.

The OCaml version of \name and all OCaml benchmarks
were compiled with 4.14.1+BER MetaOCaml \texttt{ocamlopt}, the native code compiler for OCaml, using compiler flag \texttt{-O3}.
The baseline OCaml generators were written with \bq{} 0.16.
The Scala 3 version of \name and all Scala benchmarks
were run on Scala 3.6.3
and OpenJDK 21.0.6, using ScalaCheck version 1.17 as the baseline.
We used \texttt{core\_bench} 0.16 \cn in OCaml and \texttt{jmh} 0.4.7 \cn for generator performance microbenchmarking.
